Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-04-08 Cost_manuscript.Rmd
draft from btw-subj results complete

  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the effort groups. Figure 3 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle). One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`). Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp)`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`). It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05). The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.

  We repeated these pairwise permutations to identify differences in earnings. In line with the earnings results from the previous section, the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`). In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).

@@

# and plot
(hrPlot_btw <- dataBtw %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
        summarise(pAccept = mean(Choice)) %>%
        group_by(Cost, Handling, Offer, optimal) %>%
        summarise(meanComplete = mean(pAccept),
                  SE = sd(pAccept) / sqrt(length(pAccept))) %>%
   ggplot(aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Offer.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = colsBtw) +
        theme(legend.key = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16)))

@@

``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
mixLogis_main <- list()
mixData <- dataBtw %>%
  #filter(Choice < 2) %>% analysis performed on acceptances, not completions
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice)) %>%
  ungroup()

@@

# matrix of coefficients and pvalues
rearrange <- c("Cognitive", "Easy", "Wait", "Physical") # to kinda match the order in Cost 3
mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
diag(mixSummary$Pvals) <- NA

@@

@@

``` {r BTW: 16.2.4. Plot Deviance comparison, echo = FALSE, fig.align = "center", fig.width = 6,fig.height = 4}
# plot AIC and BIC
(mixLogis_compare$plot <- ME_evals$abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    theme_classic())

@@

  However, our hypothesis stated that differences in cost would be uniform across handling times and rewards. We therefore distilled the previous analysis to examine choice behavior for every combination of experimental parameters. Figure X shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition, with optimal acceptance rates depicted by the gray circles. Qualitatively, the figure confirms two important predictions. First, participants adapted to the richness of the each timing block, showing a pattern of acceptances that resembled the optimal strategy regardless of the cost they faced. Second, differences in cost were consistent across blocks, and acceptances were highest for the cognitive effort group. The optimality of the strategies produced by each cost depended on the richness of the block. This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.

  In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details). As predicted, and confirming previous results, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`). In order to show the comparisons among all conditions, Figure X portrays the coefficients (color scale **maybe exponentiated coefficients to make it more intuitive?**), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons). Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group. The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.

  We next examined whether choice behavior could be better explained by environmental statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices. Figure X shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details). Here we focus on AIC, as both metrics yielded comparable results. As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a_priori~ = `r ME_evals$abicLogis_compare["AllMain", "AIC"]`, AIC~handling/reward~ = `r ME_evals$abicLogis_compare["HR", "AIC"]`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r ME_evals$HRvMain$Chisq[2]`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`). However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r ME_evals$abicLogis_compare["HR_interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r ME_evals$MainvHRint$Chisq[2]`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r ME_evals$abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r ME_evals$MainvAllint$Chisq[2]`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`). These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001). As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior comes from the a priori model containing all main effects. In combination with the pattern observed in Figure X, these results confirm that handling and reward amounts were similarly integrated across groups, but that the absolute rate of acceptances was affected by the cost faced (and was highest for those confronted with cognitive demands).

@@

``` {r BTW: 16.3.1. RTs, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# qualitative survival analysis
# this version of a survival curve forces all successful acceptances to have an RT of 14 (i.e. the longest handling time)
# that's to avoid jumps from 2s to 10s to 14s
# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
temp <- dataBtw %>%
    #filter(rawChoice < 2) %>% 
    mutate(#RT = ifelse(Choice == 1, 14, RT),
           Choice = 1 - Choice)

@@

survPlot_btw <- autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = colsBtw) +
  scale_fill_manual(values = colsBtw) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
  theme(legend.position = c(0.35, 0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))

# supplemental
# RT ecdfs for the whole group across blocks, with the option to subdivide by cost group
RTplot_btw <- dataBtw %>%
  filter(Choice == 0,
         RT < 1) %>%
  ggplot(aes(RT, group = Block, color = Block)) +
    stat_ecdf() +
    labs(y = "Proportion of Quits Before Time X", x = "Quitting Time") +
    facet_wrap(vars(Cost)) +
    theme_classic()

survPlot_btw | RTplot_btw

@@

# and plot
prepost_btw$scatterplot <- dataBtw %>%
                        filter(Choice < 2) %>%
                        group_by(SubjID, Cost) %>%
                        summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
                                  propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
                        ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                          geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
                          scale_fill_manual(values = colsBtw) +
                          scale_color_manual(values = colsBtw) +
                          xlim(0, 1) +
                          ylim(0, 1) +
                          labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                          geom_abline(slope = 1, intercept = 0, lty = 2) +
                          geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
                          geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
                          theme(panel.grid.major = element_blank(),
                                panel.grid.minor = element_blank(),
                                panel.background = element_blank(),
                                axis.line = element_line(colour = "black"),
                                text = element_text(size = 16))

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost_btw$propBlocks <- dataBtw %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs_btw)) %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = colsBtw) +
                           scale_fill_manual(values = colsBtw) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.25),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 16))

prepost_btw$scatterplot | prepost_btw$propBlocks
```

@@

  Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment. Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment. We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure X, left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels. This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time. Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line). This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code). Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure X, right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed (note that participants in physical conditions mostly relied on letting the grace period expire). These response time observations suggest clarity in participant preferences.

  We next examined the second prediction (i.e. strategy stability) by comparing acceptances rates throughout the experiment. The scatter plot on Figure X shows the overall proportion accepted by each participant before and after the mid-point break (colored dashed lines indicate the mean for that group). Paired permutations on means of proportions showed no differences for wait and easy groups (*p* > 0.05), but significantly lower acceptance rates for physical (*p* = `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* = `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups. The decline in acceptances appeared to be gradual for the cognitive group, but not for the physical group (Figure X, half point indicated by the dashed line). An explanation for these results is that these conditions became costlier due to fatigue, thus providing evidence that our cognitive and physical manipulations were effortful.

>>>>

  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the effort groups. Figure 3 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle). One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`). Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`). It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05). The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.

  We repeated these pairwise permutations to identify differences in earnings. In line with the earnings results from the previous section, the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`). In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).

@@

# and plot
hrPlot_btw <- dataBtw %>%
        filter(Choice < 2) %>%
        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
        summarise(pAccept = mean(Choice)) %>%
        group_by(Cost, Handling, Offer, optimal) %>%
        summarise(meanComplete = mean(pAccept),
                  SE = sd(pAccept) / sqrt(length(pAccept))) %>%
   ggplot(aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
        geom_point(size = 3) + 
        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
        labs(x = "Offer.Handling", y = "Proportion Accepted") +
        scale_color_manual(values = colsBtw) +
        theme(legend.key = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 12))

@@

``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4, include = FALSE}
# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
mixLogis_main <- list()
mixData <- dataBtw %>%
  #filter(Choice < 2) %>% analysis performed on acceptances, not completions
  group_by(SubjID, Cost, Handling, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice)) %>%
  ungroup()

@@

# matrix of coefficients and pvalues
rearrange <- c("Cognitive", "Easy", "Wait", "Physical") # to kinda match the order in Cost 3
mixSummary_btw <- betaMatrix(mixLogis_main, rearrange = rearrange)
diag(mixSummary_btw$Pvals) <- NA

@@

corrplot(mixSummary_btw$Betas, 
         is.corr = F, 
         p.mat = mixSummary_btw$Pvals, 
         type = "lower",
         outline = T,
         #insig = "p-value",
         sig.level = 0.05, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))

@@

``` {r BTW: 16.2.4. Plot Deviance comparison, echo = FALSE, fig.align = "center", fig.width = 6,fig.height = 4}
# plot AIC and BIC
ABIC_plot_btw <- ME_evals$abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
      theme(legend.position = c(0.8, 0.7),
            axis.text.x = element_text(angle = 45, hjust = 1),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.background = element_blank(),
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))

@@

```{r mixed effects plots (Fig. 4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination. A:  B:  Each entry shows how much more likely was the reference group to accept an offer than the comparison group. C:"}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG4.png")
```

  However, our hypothesis stated that differences in cost would be uniform across handling times and rewards. We therefore distilled the previous analysis to examine choice behavior for every combination of experimental parameters. Figure 4A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost, with optimal acceptance rates depicted by the gray circles. Qualitatively, the figure confirms two important predictions. First, participants adapted to the richness of the each timing block, showing a pattern of acceptances that resembled the optimal strategy regardless of the cost they faced. Second, differences in cost were consistent across blocks, and acceptances were highest for the cognitive effort group. The optimality of the strategies produced by each cost depended on the richness of the block. This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.

  In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details). As predicted, and confirming previous results, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`). In order to show the comparisons among all conditions, Figure 4B portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons). The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.

  We next examined whether choice behavior could be better explained by environmental statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices. Figure 4C shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details). Here we focus on AIC, as both metrics yielded comparable results. As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`). However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`). These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001). As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior comes from the a priori model containing all main effects. In combination with the pattern observed in Figure 4A, these results confirm that handling and reward amounts were similarly integrated across groups, but that the absolute rate of acceptances was affected by the cost faced (and was highest for those confronted with cognitive demands).

@@

``` {r BTW: 16.3.1. surv and RTs, echo = FALSE, warning = FALSE, fig.align = "center", fig.width = 10, fig.height = 4, include = FALSE}
# qualitative survival analysis
# this version of a survival curve forces all successful acceptances to have an RT of 14 (i.e. the longest handling time)
# that's to avoid jumps from 2s to 10s to 14s
# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
temp <- dataBtw %>%
    #filter(rawChoice < 2) %>% 
    mutate(#RT = ifelse(Choice == 1, 14, RT),
           Choice = 1 - Choice)

@@

survPlot_btw <- autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = colsBtw) +
  scale_fill_manual(values = colsBtw) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 14))

# supplemental
# RT ecdfs for the whole group across blocks, with the option to subdivide by cost group
RTplot_btw <- dataBtw %>%
  filter(Choice == 0,
         RT < 1) %>%
  ggplot(aes(RT, group = Block, color = Block)) +
    stat_ecdf() +
    scale_x_continuous(breaks = seq(0, 1, length.out = 3), labels = c(0, 0.5, 1)) +
    labs(y = "Proportion of Quits Before Time X", x = "Quitting Time (seconds)") +
    facet_wrap(vars(Cost)) +
    theme(#legend.position = c(0.9, 0.7),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 14))

@@

# and plot
prepost_btw$scatterplot <- dataBtw %>%
                        filter(Choice < 2) %>%
                        group_by(SubjID, Cost) %>%
                        summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
                                  propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
                        ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
                          geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
                          scale_fill_manual(values = colsBtw) +
                          scale_color_manual(values = colsBtw) +
                          xlim(0, 1) +
                          ylim(0, 1) +
                          labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                          geom_abline(slope = 1, intercept = 0, lty = 2) +
                          geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
                          geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
                          theme(panel.grid.major = element_blank(),
                                panel.grid.minor = element_blank(),
                                panel.background = element_blank(),
                                axis.line = element_line(colour = "black"),
                                text = element_text(size = 14))

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost_btw$propBlocks <- dataBtw %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs_btw)) %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = colsBtw) +
                           scale_fill_manual(values = colsBtw) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.25),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 14))

@@

```{r Survival and prepost plots (Fig. 5), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time. Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each group. On the right, the proportion accepted over time per group. The order of blocks was repeated in the second half (indicated by the black dashed line)."}
# plots generated in 16.3.1. and 16.3.2.
(suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
```

  Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment. Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment. We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels. This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time. Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line). This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code). Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed. These response time observations suggest clarity in participant preferences.
